UNet-HCRF Integration for EEG Pattern Recognition

### 2024-12-09 manuscript/slides.tex
revise title
typo

\title[\textcolor{black}{UNet-HCRF\_EEG}]{\large
UNet-HCRF Integration for Sequence Labeling on EEG Data}

@@

\begin{frame}{Results}
We evaluate our model by 5 fold cross-validation.
\bigskip
\begin{itemize}
\item Our model achieves a \textbf{0.4992} KL-divergence.
\bigskip
\item The baseline model from Kaggle using EfficientNet obtains a 0.59
cross-validation KL-divergence.
\end{itemize}
\bigskip
However, there still are many teams on Kaggle have achieved even lower
KL-divergence scores (0.2-0.3) by leveraging the power of large models
like Vision Transformers (ViT).
\end{frame}

>>>>

\title[\textcolor{black}{UNet-HCRF\_EEG}]{
UNet-HCRF Integration for EEG Pattern Recognition}

@@

\begin{frame}{Results}
We evaluate our model by 5 fold cross-validation.
\bigskip
\begin{itemize}
\item Our model achieves a \textbf{0.4992} KL-divergence.
\bigskip
\item The baseline model from Kaggle using EfficientNet obtains a 0.59
cross-validation KL-divergence.
\end{itemize}
\bigskip
However, many teams on Kaggle have achieved even lower
KL-divergence scores (0.2-0.3) by leveraging the power of large models
like Vision Transformers (ViT).
\end{frame}
